Title here

### 2020-08-24 paper/paper.Rmd
minor fixes section 1

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their initial paper on projection pursuit in 1974 that "the  technique  used  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied to more generally to help practitioner to unveil the black-box in randomised iterative (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont, bbm}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

The remainder of the paper is organised as follows. 
Section \ref{optim} provides the literature review of optimisation methods, specifically the line search methods used in projection pursuit guided tour. 
Section \ref{tour} reviews projection pursuit guided tour, forms the optimisation problem, and introduces three main existing algorithms.
Section \ref{vis-diag} presents the new visual diagnostics design, from forming the data object to the definition of different diagnostic plots with some small examples. 
Section \ref{application} shows the applicaiton of how the diagnostic plots designed in section \ref{vis-diag} can be used to understand and compare different algorithms and how they contribute to modifications that improve the algorithms.
Finally, Section \ref{implementation} describes the R package: ferrn, that implements all the visual diagnostics above.

@@

Modern development of the line search methods focuses on proposing different computation on the seraching direction: $d^{(j)}$ and various approximations on the step size: $\alpha_j$ catered for practical optimisation problems. The specific problem context we are interested in is called projection pursuit guided tour. 
Projection pursuit and guided tour are two separate methods in exporatory data analysis focusing on different aspects: coined by @friedman1974projection, projection pursuit detects interesting structures (i.e. clustering, outliers and skewness) in multivariate data via low dimensions projection; whilst guided tour is a particular variation in a broader class of data visualisation method called tour.

>>>>

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their initial paper on projection pursuit in 1974 that "the  technique  used  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied more generally to help practitioner to unveil the black-box in randomised iterative (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont, bbm}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

The remainder of the paper is organised as follows. 
Section \ref{optim} provides a literature review of optimisation methods, specifically the line search methods used in projection pursuit guided tour. 
Section \ref{tour} reviews projection pursuit guided tour, forms the optimisation problem, and introduces three main existing algorithms.
Section \ref{vis-diag} presents the new visual diagnostics design, from forming the data object to the definition of different diagnostic plots with some small examples. 
Section \ref{application} shows the application of how the diagnostic plots designed in section \ref{vis-diag} can be used to understand and compare different algorithms and how they contribute to modifications that improve the algorithms.
Finally, Section \ref{implementation} describes the R package: ferrn, that implements all the visual diagnostics above.

@@

Modern development of the line search methods focuses on proposing different computation on the searching direction: $d^{(j)}$ and various approximations on the step size: $\alpha_j$ catered for practical optimisation problems. The specific problem context we are interested in is called projection pursuit guided tour. 
Projection pursuit and guided tour are two separate methods in exporatory data analysis focusing on different aspects: coined by @friedman1974projection, projection pursuit detects interesting structures (i.e. clustering, outliers and skewness) in multivariate data via low dimensions projection; whilst guided tour is a particular variation in a broader class of data visualisation method called tour.
